Differential Host Competence of Amphibian Communities for Ranavirus

### 2023-02-14 scripts/workshop/community_final.Rmd
update pathname

Ranavirus Summary
```{r, Ranavirus Summary}
data <- read_csv("competence.csv")

@@

```
Same summary as before but with a different measure of competency. These measures are calculated using only RV positive individuals
```{r, Ranavirus Summary 2}
data <- read_csv("competence_rv_pos.csv")

>>>>

Ranavirus Summary
```{r, Ranavirus Summary}
data <- read_csv("/Users/dcsuh/Documents/GitHub/rana-competence/data/raw_data/competence.csv")

@@

Same summary as before but with a different measure of competency. These measures are calculated using only RV positive individuals

```{r, Ranavirus Summary 2}
data <- read_csv("competence_rv_pos.csv")
